An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-29 VLDB2026/main.tex
Update main.tex

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
		\caption{Hybrid query example}

@@

		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.02cm}
		\caption{Graph index and IVF index}

@@

	\setlength{\textfloatsep}{0cm}
	\setlength{\floatsep}{0cm}
	\renewcommand{\arraystretch}{0.9}
	\begin{table*}[t]
		\centering
		%\setlength{\belowcaptionskip}{-0.3cm}
		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Comparison of AF-ANN search algorithms}
		\small
		\label{tab:compair_1}
		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			NHQ & Graph & C & Y & N& N& N & N & N \\
			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\

@@

		\centering
		%	 \setlength{\abovecaptionskip}{0cm}
		%	\setlength{\belowcaptionskip}{0.1cm}
		\footnotesize{
			\begin{minipage}{\linewidth}
				\vspace{0.1cm}
				\textsuperscript{A} Post-filtering, 
				\textsuperscript{B} Pre-filtering, 
				\textsuperscript{C} Simultaneous filtering, 
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport. 
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
				\textit{OR} indicates whether the algorithm supports attribute filtering with OR operations. 
				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
				\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
		\end{minipage}}
		\vspace{-0.5cm}
	\end{table*}

@@

	\setlength{\textfloatsep}{0.1cm}
	\setlength{\floatsep}{0cm}
	\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.1cm}
		\setlength{\textfloatsep}{0.1cm}
		\caption{Comparison of RF-ANN search algorithms}
		\small	% 只会影响当前组的内容
		\label{tab:range_algo}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			DSG & Graph & Y & N \\
			iRange & Graph & N & Y \\
			SeRF & Graph & Y & Y \\
			UNIFY & Graph & Y & Y \\
			WinFilter & Graph & N & Y  \\
			\hline
		\end{tabular}

		\footnotesize{
			\begin{minipage}{\linewidth}
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport.
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
			\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
			\end{minipage} 
			\vspace{-0.1cm}
		}

@@

	\setlength{\textfloatsep}{0.1cm}
	\setlength{\floatsep}{0cm}
	\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering

		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.3cm}
		\caption{Datasets}

@@

	%4.2.1
	\subsubsection{Time and Space overhead of index construction}
	% \subsubsection{\textbf{Attribute Filtering}}
	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.3cm}
		\setlength{\belowcaptionskip}{-0.0cm}

@@

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{-0.02cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Index construction time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{-0.02cm}
			\setlength{\belowcaptionskip}{-0.1cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{Index size}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{-0.02cm}
			\setlength{\belowcaptionskip}{-0.3cm}
			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Peak memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

@@

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Single-Attribute Building and Query (single thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
		\caption{Single-Attribute Building and Query (16 threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

	\begin{figure}[t]
		\centering
		\setlength{\abovecaptionskip}{0.1cm}
		\setlength{\belowcaptionskip}{-0.1cm}
		% 上面的图例，居中并可通过 hspace 调整左右位置
		\hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
		\includegraphics[width=0.85\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径

@@

	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.  CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping. In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs. 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness. 4) UNG has poor performance because large number of entry points that need to be traversed. It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates. The performance of CAPS is as good as that of Puck. The difference between them is that CAPS further groups the results by attributes within clusters. In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0.0cm}
		\setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
		\caption{Multi-attribute build and query (single thread)}
		\label{fig:exp_4_1_MultiLabel_1thread}
	\end{figure*}

	\begin{figure*}
		\centering
		\setlength{\abovecaptionskip}{0.0cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects \textcolor{red}{real-world scenarios}. To evaluate algorithm performance \textcolor{red}{under this setting}, we construct the index using 3 uniformly distributed attributes and \textcolor{red}{apply filtering on all 3 attributes simultaneously during queries}.
	 \textcolor{red}{As Filtered-DiskANN does not support the AND rule used in our multi-attribute queries, it is excluded.}
	%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

@@

	To investigate this effect, we evaluate 4 AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset. Using a single-thread execution environment, we compare the query performance of attribute filtering algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.

@@

		% 第一行：单独一张大图
		\begin{subfigure}{\textwidth}
			\centering
			\setlength{\abovecaptionskip}{0.05cm}
			\setlength{\belowcaptionskip}{0.05cm}
			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
			\caption{Algorithms optimized for low AS levels.}
			\label{fig:exp_5_2_1}
		\end{subfigure}

@@

		% 第二行：两张子图，左侧宽度是右侧的两倍
		\begin{subfigure}{0.64\textwidth} % 2/3 宽度
			\centering
			\setlength{\abovecaptionskip}{0.05cm}
			\setlength{\belowcaptionskip}{0.05cm}
			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_2.pdf}
			\caption{Algorithms optimized for high AS levels.}
			\label{fig:exp_5_2_2}
		\end{subfigure}
		\hspace{1mm} % 增加水平间距
		\begin{subfigure}{0.32\textwidth} % 1/3 宽度
			\centering
			\setlength{\abovecaptionskip}{0.05cm}
			\setlength{\belowcaptionskip}{0.05cm}
			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_3.pdf}
			\caption{Algorithms insensitive to AS level.}
			\label{fig:exp_5_2_3}
		\end{subfigure}

		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.4cm}
		\caption{Different AS under the same algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

	\begin{figure*}
		\centering
		    \setlength{\abovecaptionskip}{-0.1cm}
		    \setlength{\belowcaptionskip}{-0.4cm}
		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of dataset on Query}
		\label{fig:exp_6_1}
	\end{figure*}

@@

		\setlength{\abovecaptionskip}{0.02cm}
		\setlength{\belowcaptionskip}{-0.1cm}
		\hspace*{11pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.90\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

@@

		% 三图横排
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\captionsetup{font=small}
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{\footnotesize Construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\setlength{\abovecaptionskip}{0.02cm}
			\setlength{\belowcaptionskip}{0.02cm}
			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{\footnotesize Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

@@

		\centering
		\setlength{\abovecaptionskip}{0cm}
		\setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{RF-ANN search }
		\label{fig:exp_8_2}
	\end{figure*}

@@

	% \begin{figure*}[htbp]
		%     \centering
		%     \setlength{\abovecaptionskip}{0cm}
		%     \setlength{\belowcaptionskip}{-0.4cm}
		%     \includesvg[width=\textwidth]{figures/exp/exp_8_3.svg}
		%     \caption{Dataset Effect on RF-ANN Search}
		%     \label{fig:exp_8_3}
		% \end{figure*}
	\begin{figure*}[htbp]
		\centering
		    \setlength{\abovecaptionskip}{0cm}
		    \setlength{\belowcaptionskip}{-0.5cm}
		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

@@

	\begin{table}[t]
		\centering
		\setlength{\abovecaptionskip}{0.0cm}
		\caption{Algorithm Recommendation per Scenario}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{|l|c|c|}
				\hline
				\textbf{Scenario} & \textbf{Attribute Filtering} & \textbf{Range Filtering}\\
				\hline
				S1: Large-scale Datasets & Puck, UNG & iRange\\[1pt]
				\hline
				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\[1pt]
				\hline
				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\[1pt]
				\hline
				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\[1pt]

				\hline
				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\[1pt]
				\hline
				S6: Resource constraint& CAPS, Faiss&Faiss, SeRF \\[1pt]
				\hline
				S7: High-Recall Querying & UNG & WinFilter \\[1pt]
				\hline
				S8: OOD scenarios & UNG &WinFilter  \\[1pt]
				\hline
			\end{tabular}
		}
		\label{tab:algo_scenarios}
	\vspace{-0.0cm}
	\end{table}

>>>>

		\includegraphics[width=0.92\textwidth]{figures/hybrid ANNS.pdf}
		\caption{Hybrid query example}

@@

		\caption{Graph index and IVF index}

@@

	\renewcommand{\arraystretch}{0.9}
	\begin{table*}[t]
		\centering
		%\setlength{\belowcaptionskip}{-0.3cm}

		\caption{Comparison of AF-ANN search algorithms}
		\small
		\label{tab:compair_1}
		\begin{tabular}{|l|l|c|c|c|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Filter Type} & \textbf{AND} & \textbf{OR} & \textbf{Flexible Attributes} & \textbf{Complex Boolean} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			NHQ & Graph & C & Y & N& N& N & N & N \\
			FilteredVamana & Graph & C & N & Y & Y & N & Y & Y \\
			StitchedVamana & Graph & C & N & Y & Y & N & N & Y  \\
			CAPS & IVF & C & Y & N & Y & N & Y & Y \\
			ACORN & Graph & B & Y & Y & Y & Y & Y & Y \\
			UNG & Graph & B & Y & Y & Y & N & Y & Y \\ 
			Puck & IVF & B & Y & Y & Y & N & Y & Y \\
			% ParlayANN & Graph+IVF & B & N & N & Y & N & N & Y \\

@@

		\centering
		%	 \setlength{\abovecaptionskip}{0cm}
		%	\setlength{\belowcaptionskip}{0.1cm}
		\footnotesize{
			\begin{minipage}{\linewidth}
				\vspace{0.1cm}
				\textsuperscript{A} Post-filtering, 
				\textsuperscript{B} Pre-filtering, 
				\textsuperscript{C} Simultaneous filtering, 
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport. 
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{AND} indicates whether the algorithm supports attribute filtering with AND operations. 
				\textit{OR} indicates whether the algorithm supports attribute filtering with OR operations. 
				\textit{Flexible Attributes} indicates whether the number of query attributes can differ from the number of attributes used during index construction. 
				\textit{Complex Boolean} refers to whether the algorithm supports advanced Boolean logic beyond just AND and OR, such as NOT or combinations like (A AND B) OR (C AND NOT D). 
				\textit{Dynamic Insert} indicates whether the algorithm supports the operation of dynamically inserting data points.
				\textit{Multi Thread} indicates whether the algorithm supports multi-threaded search.
		\end{minipage}}

	\end{table*}

@@

	\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering

		\setlength{\textfloatsep}{0.1cm}
		\caption{Comparison of RF-ANN search algorithms}
		\small	% 只会影响当前组的内容
		\label{tab:range_algo}
		\begin{tabular}{|c|c|c|c|}
			\hline
			\textbf{Algorithm} & \textbf{Base} & \textbf{Dynamic Insert} & \textbf{Multi Thread} \\
			\hline
			DSG & Graph & Y & N \\
			iRange & Graph & N & Y \\
			SeRF & Graph & Y & Y \\
			UNIFY & Graph & Y & Y \\
			WinFilter & Graph & N & Y  \\
			\hline
		\end{tabular}

		\footnotesize{
			\begin{minipage}{\linewidth}
				\textsuperscript{Y} Support, 
				\textsuperscript{N} Unsupport.
				\textit{Base} indicates that the hybrid query algorithm is an improvement based on a specific ANN search algorithm. 
				\textit{Dynamic} indicates whether the algorithm supports the operation of dynamically inserting data points.
			\end{minipage}

		}

@@

	\renewcommand{\arraystretch}{0.9}
	\begin{table}[t]
		\centering

		\caption{Datasets}

@@

	%4.2.1
	\subsubsection{Time and Space overhead of index construction}
	% \subsubsection{\textbf{Attribute Filtering}}
	\begin{figure}[t]
		\centering

@@

		\begin{subfigure}{\columnwidth}
			\centering

			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_build_time_comparison_query1.pdf}
			\caption{Index construction time}
			\label{fig:build_time_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering

			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_index_size_mb_comparison_query1.pdf}
			\caption{Index size}
			\label{fig:index_size_mb_comparison_query1}
		\end{subfigure}

		\begin{subfigure}{\columnwidth}
			\centering

			\includegraphics[width=0.95\linewidth]{figures/indexData/exp_7_memory_mb_comparison_query1.pdf}
			\caption{Peak memory usage}
			\label{fig:memory_mb_comparison_query1}
		\end{subfigure}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_1_SingleLabel_1thread.pdf}
		\caption{Single-Attribute Building and Query (single thread) }
		\label{fig:exp_1_1_SingleLabel_1thread}
	\end{figure*}

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_1_2_SingleLabel_16thread.pdf}
		\caption{Single-Attribute Building and Query (16 threads)}
		\label{fig:exp_1_2_SingleLabel_16thread}
	\end{figure*}

@@

		% 上面的图例，居中并可通过 hspace 调整左右位置
		\hspace*{15pt} % 可调整的参数，负值左移，正值右移，例如 -20pt 或 20pt
		\includegraphics[width=0.85\columnwidth]{figures/exp/exp_2_legend.pdf} % 图例图片路径

@@

	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation. In contrast, CAPS shows a slight performance decline due to the increased query overhead caused by excessive attribute-based grouping. Compared with CAPS, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs. 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness. 4) UNG has poor performance because large number of entry points that need to be traversed. It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.

	\textit{Performance of Algorithms under Multi-Attribute Building (M vs. M).}  
	As shown in Figure \ref{fig:exp_2_1}, IVF-based methods (Puck and CAPS) significantly outperform graph-based methods. The reason for Puck's superior performance is that it filters out irrelevant results during the retrieval process rather than searching for more candidates. The performance of CPAS is as good as that of Puck. The difference between them is that CPAS further groups the results by attributes within clusters. In contrast, FilteredVamana performs the worst because its multi-attribute indexing forces neighbor selection to cover multiple attributes, thereby reducing the efficiency of single-attribute queries. This results in excessive traversal of irrelevant nodes, making it slower than other methods.

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_4_1_MultiLabel_1thread.pdf}
		\caption{Multi-attribute build and query (single thread)}
		\label{fig:exp_4_1_MultiLabel_1thread}
	\end{figure*}

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_3_1.pdf}
		\caption{Effect of attribute distribution on query performance (single thread)}
		\label{fig:exp_3_1}
	\end{figure*}

	\textit{\textbf{Multi-Attribute Building and Multi-Attribute Query.}}  
	Compared to single-attribute filtering, multi-attribute joint filtering better reflects \textcolor{red}{real-world scenarios}. To evaluate algorithm performance \textcolor{red}{under this setting}, we construct the index using 3 uniformly distributed attributes and \textcolor{red}{apply filtering on all 3 attributes simultaneously during queries}.
%	Compared to single-attribute filtering, multi-attribute joint filtering better reflects real-world application scenarios. To evaluate algorithm performance under such scenario, we construct the index using 3 uniformly distributed attributes and apply filtering conditions on all 3 attributes simultaneously during the query process.

@@

	To investigate this effect, we evaluate 4 AS levels (1\%, 25\%, 50\%, and 75\%) on the SIFT1M dataset. Using a single-thread execution environment, we compare the query performance of 13 algorithms under varying AS conditions, as shown in Figure~\ref{fig:exp_5_1_1_SingleLabel_1thread}.

@@

		% 第一行：单独一张大图
		\begin{subfigure}{\textwidth}
			\centering

			\includegraphics[width=0.95\textwidth]{figures/exp/exp_5_2_1.pdf}
			\caption{Algorithms optimized for low AS levels.}
			\label{fig:exp_5_2_1}
		\end{subfigure}

@@

		% 第二行：两张子图，左侧宽度是右侧的两倍
		\begin{subfigure}{0.64\textwidth} % 2/3 宽度
			\centering

			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_2.pdf}
			\caption{Algorithms optimized for high AS levels.}
			\label{fig:exp_5_2_2}
		\end{subfigure}
		\hspace{1mm} % 增加水平间距
		\begin{subfigure}{0.32\textwidth} % 1/3 宽度
			\centering

			\includegraphics[width=0.92\textwidth]{figures/exp/exp_5_2_3.pdf}
			\caption{Algorithms insensitive to AS level.}
			\label{fig:exp_5_2_3}
		\end{subfigure}

		\caption{Different AS under the same algorithm}
		\label{fig:exp_5_2_combined}
	\end{figure*}

@@

		\includegraphics[width=0.95\textwidth]{figures/exp/exp_6_1.pdf}
		\caption{Effect of dataset on Query}
		\label{fig:exp_6_1}
	\end{figure*}

@@

		\hspace*{11pt}
		% 放大的图例（占满单栏）
		\includegraphics[width=0.90\columnwidth]{figures/indexData/rangeFilter_legend_only.pdf}

@@

		% 三图横排
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering
			\captionsetup{font=small}

			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_build_time_comparison_query.pdf}
			\caption{\footnotesize Construction time}
			\label{fig:rangeFilter_build_time}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering

			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_index_size_mb_comparison_query.pdf}
			\caption{\footnotesize Index size}
			\label{fig:rangeFilter_index_size_mb}
		\end{subfigure}
		\hfill
		\begin{subfigure}[t]{0.32\columnwidth}
			\centering

			\includegraphics[width=\linewidth]{figures/indexData/rangeFilter_memory_mb_comparison_query.pdf}
			\caption{\footnotesize Peak memory usage}
			\label{fig:rangeFilter_memory_mb}
		\end{subfigure}

@@

		\centering

		\includegraphics[width=0.92\textwidth]{figures/exp/exp_8_2.pdf}
		\caption{RF-ANN search }
		\label{fig:exp_8_2}
	\end{figure*}

@@

	\begin{figure*}[htbp]
		\centering

		\includegraphics[width=0.80\textwidth]{figures/exp/exp_8_3.pdf}
		\caption{Dataset Effect on RF-ANN Search}
		\label{fig:exp_8_3}
	\end{figure*}

@@

	\begin{table}[t]
		\centering

		\caption{Algorithm Recommendation per Scenario}
		\resizebox{\columnwidth}{!}{
			\begin{tabular}{|l|c|c|}
				\hline
				\textbf{Scenario} & \textbf{Attribute Filtering} & \textbf{Range Filtering}\\
				\hline
				S1: Large-scale Datasets & Puck, UNG & iRange\\[1pt]
				\hline
				S2: Fast Index Construction & ACORN-1, UNG  &Faiss\\[1pt]
				\hline
				S3: Query on Hard Datasets & CAPS, UNG &WinFilter, iRange, DSG\\[1pt]
				\hline
				S4: Query on Easy Datasets & StitchedVamana, NHQ, UNG & WinFilter, iRange\\[1pt]

				\hline
				S5: General-purpose Use & Milvus, Faiss &DSG, UNIFY\\[1pt]
				\hline
				S6: Resource constraint& CAPS, Faiss&Faiss, SeRF \\[1pt]
				\hline
				S7: High-Recall Querying & UNG & WinFilter \\[1pt]
				\hline
				S8: OOD scenarios & UNG &WinFilter  \\[1pt]
				\hline
			\end{tabular}
		}
		\label{tab:algo_scenarios}
	\end{table}
